%%% vim:ai:tw=72:
\chapter{Intel LAM Extension}

\section{Intel LAM}

Intel LAM (Linear Address Masking) Extension allows software to locate
metadata in data pointers and dereference them without needing to mask
the metadata bits.  It supports:

\begin{description}
  \item[LAM_U48] Activate LAM for user data pointers and use of bits
    62:48 as masked metadata.
  \item[LAM_U57] Activate LAM for user data pointers and use of bits
    62:57 as masked metadata.
\end{description}

\section{Program Loading}

\subsection{Process \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U48}}
\label{lam_u48}

On an LAM capable processor, the following steps should be taken:

\begin{enumerate}
  \item
    \begin{sloppypar}
      When loading an executable without interpreter, enable LAM_U48
      if \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U48} is set on the
      executable.
    \end{sloppypar}
  \item
    \begin{sloppypar}
      When loading an executable with an interpreter, enable LAM_U48
      if \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U48} is set on the
      interpreter.  The interpreter should disable LAM_U48 if
      \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U48} isn't set on the
      executable or any shared objects loaded via the \code{DT_NEEDED}
      tag.
    \end{sloppypar}
  \item
    \begin{sloppypar}
      After LAM_U48 is enabled, when loading a shared object without
      \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U48}:
      \begin{enumerate}
	\item If legacy interwork is allowed, LAM_U48 should be disabled.
	\item If legacy interwork isn't allowed, it causes an error.
      \end{enumerate}
    \end{sloppypar}
\end{enumerate}

\subsection{Process \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U57}}
\label{lam_u57}

On an LAM capable processor, the following steps should be taken:

\begin{enumerate}
  \item
    \begin{sloppypar}
      When loading an executable without interpreter, enable LAM_U57
      if \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U57} is set on the
      executable.
    \end{sloppypar}
  \item
    \begin{sloppypar}
      When loading an executable with an interpreter, enable LAM_U57
      if \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U57} is set on the
      interpreter.  The interpreter should disable LAM_U57 if
      \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U57} isn't set on the
      executable or any shared objects loaded via the \code{DT_NEEDED}
      tag.
    \end{sloppypar}
  \item
    \begin{sloppypar}
      After LAM_U57 is enabled, when loading a shared object without
      \code{GNU_PROPERTY_X86_FEATURE_1_LAM_U57}:
      \begin{enumerate}
	\item If legacy interwork is allowed, LAM_U57 should be disabled.
	\item If legacy interwork isn't allowed, it causes an error.
      \end{enumerate}
    \end{sloppypar}
\end{enumerate}

\code{GNU_PROPERTY_X86_FEATURE_1_LAM_U48} implies
\code{GNU_PROPERTY_X86_FEATURE_1_LAM_U57}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "abi"
%%% End:
